Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
new soa algos

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task. 
An overview of the efforts for the latter task is provided by the DCASE2013 challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms where most \ja{?} of scene predictions are achieved by majority voting of predictions over features. \ja{What about the other algorithms? Why are we excluding them here?}

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\end{tabular}
\end{center}
\caption{Algorithms evaluated on the DCASE2013 ASC private DCASE2013 dataset. RQA stands for recurrence quantification analysis, ILD for inter-aural differences and UL for unsupervised learning. Algorithms above the horizontal line participated to the DCASE challenge. Others used the private dataset afterward.  \label{tab:dcase}}
\end{table}

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. \ja{It's not clear to me how the first part implies the second part here} Similarly, we have picked SVMs as our classifier for the ASC task, since these are a standard tool in the community and allows for us to focus our analysis on the earlier processing stages. Moreover, since MFCCs are well-established features which perform well for these task, we shall include them baseline features in all experiments described in this paper.

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type.
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a fivefold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

The DCASE2013 dataset has significant intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}. In addition, it is still challenging, with a state-of-the-art system based on feature design \ja{?} and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge). Another system, using a HOG+SVM approach \cite{rakotomamonjy2015histogram}, achieves $75\%$ and $92\%$ on the DCASE2013 and Rouen datasets, respectively. Recent advances using hierarchical classifier architectures obtain between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}. On the Rouen dataset, the state-of-the-art is currently $95\%$ \cite{bisot2016acoustic}.

>>>>

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task. 
An overview of the efforts for the latter task is provided by the DCASE2013 challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms as well as newer systems that considered the private datset for their experiments. % where most \ja{?} of scene predictions are achieved by majority voting of predictions over features. \ja{What about the other algorithms? Why are we excluding them here?}

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84 to 87 & Label Tree Embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & AMS, LDA \\
\end{tabular}
\end{center}
\caption{Algorithms evaluated on the DCASE2013 ASC DCASE2013 dataset. RQA stands for recurrence quantification analysis, ILD for inter-aural differences, AMS for amplitude Modulated Spectrum and UL for unsupervised learning. Algorithms above the horizontal line participated to the DCASE challenge. Others used the private dataset afterward and the last used the public dataset.  \label{tab:dcase}}
\end{table}

In addition, it is still challenging, with a state-of-the-art system based on feature design \ja{?} and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge). Another system, using a HOG+SVM approach \cite{rakotomamonjy2015histogram}, achieves $75\%$ and $92\%$ on the DCASE2013 and Rouen datasets, respectively. Recent advances using hierarchical classifier architectures obtain between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}. On the Rouen dataset, the state-of-the-art is currently $95\%$ \cite{bisot2016acoustic}.

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}. 
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a fivefold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

%In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. \ja{It's not clear to me how the first part implies the second part here} Similarly, we have picked SVMs as our classifier for the ASC task, since these are a standard tool in the community and allows for us to focus our analysis on the earlier processing stages. Moreover, since MFCCs are well-established features which perform well for these task, we shall include them baseline features in all experiments described in this paper.
